Implementation of poloidal density variation in collision operator

### 2018-03-05 doc/manual/version3/inputParameters.tex
Working on manual
v3 manual update

\param{withNBIspec}
{Boolean}
{\false}
{\todo{Whenever ?}}
{\todo{Write description}}

@@

\param{NBIspecZ}
{real}
{1.0}
{\todo{Whenever \parlink{RHSMode} == 1 and \parlink{withNBIspec} == \true}}
{\todo{Charge of NBI heated species, in units of the proton charge $e$.}}

@@

\param{NBIspecNHat}
{real}
{0.0}
{\todo{Whenever \parlink{RHSMode} == 1 and \parlink{withNBIspec} == \true}}
{\todo{Density of NBI heated species, in units of the reference density $\bar{n}$.}}

@@

\section{The {\ttfamily export\_f}~namelist}

>>>>

\param{withNBIspec}
{Boolean}
{\false}
{Whenever \parlink{RHSMode} == 1 and \parlink{includePhi1} == \true and \parlink{quasineutralityOption} == 1}
{When this is \true, an extra species (here called NBIspec)
  is added to the quasineutrality condition, but not as a species for
  which the DKE is solved. This is to mimic that fast ions influece
  the other species mostly via the parallel electric field, an not
  much via collisions. The NBIspec is assumed to have a density
  distribution on the flux suface proporional to $B$ (which is the
  case if all particles have zero pitch angle).}

@@

\param{NBIspecZ}
{real}
{1.0}
{Whenever \parlink{RHSMode} == 1 and \parlink{includePhi1} == \true and \parlink{quasineutralityOption} == 1}
{Charge of the fast ion species, in units of the proton charge $e$.}

@@

\param{NBIspecNHat}
{real}
{0.0}
{Whenever \parlink{RHSMode} == 1 and \parlink{includePhi1} == \true and \parlink{quasineutralityOption} == 1}
{Density of the fast ion species, in units of the reference density $\bar{n}$.}

@@

\section{The {\ttfamily export\_f}~namelist}
\label{sec:exportfParameters}
